Novakovic et al 2019 reanalysis

### 2024-01-03 figs/ART_novakovic.Rmd
fix path for idat

#targets$Basename <- gsub("IDAT/","",targets$Basename)  
birth<-targets[which(targets$`time_of_collection`=="birth"),]
birth$Basename <- sapply(strsplit(birth$Basename,"/"),"[[",3)
birth$Basename <- sapply(strsplit(birth$Basename,"_"),"[[",1)

>>>>

#targets$Basename <- gsub("IDAT/","",targets$Basename)  
birth <- targets[which(targets$`time_of_collection`=="birth"),]
birth$Basename <- sapply(strsplit(birth$Basename,"/"),"[[",2)
birth$Basename <- sapply(strsplit(birth$Basename,"_"),"[[",1)
